---
title: "Figures"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
di <- "/Users/maria.suarez.munoz/Google Drive/ms_FuzzyCognitiveMapping/FCM_analysis"
input_folder <- "input_files"
output_folder <- "output_files"

library(dplyr)
library(reshape2)
library(ggplot2)
library(plotly)
library(ggalluvial)
library(GGally)
library(scales)

# Color-blind palette: "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"

orange <- "#E69F00" # ORANGE
green <- "#009E73" # GREEN
blue <- "#0072B2" # DARK BLUE
red <- "#D55E00" # RED
```

# [Figure_FCM_scheme]

Manual

# Figure_stakeholders_alluvial

```{r}
stakeholders <- read.csv(paste(di, input_folder, "interviews_info_clean.csv", sep = "/"), sep = ";") %>%
  mutate(freq = 1,
         Type = New_stakeholders_classification)
stakeholders %>% group_by(Type, Knowledge.area...clean, Action.level) %>%
  summarise(n = sum(freq)) -> stakeholders3d

ggplot(stakeholders3d, aes(y = n, axis2 = Type, axis3 = Knowledge.area...clean, axis1 = Action.level)) +
  geom_alluvium(col = green, fill = green, alpha = 0.3) +
  geom_stratum(fill = green, color = "grey") +
  geom_text(stat = "stratum", label.strata = TRUE, size = 2) +
  scale_x_continuous(breaks = 1:3, labels = c("Action level", "Stakeholder type", "Knowledge area")) +
  scale_y_continuous(NULL, breaks = NULL) +
  theme_minimal()
```

# Figure_accumulation_curves

```{r, include=FALSE}
# load files
acc_table_whole <- read.csv(paste(di, output_folder, "3.0 acc_table_whole_community.csv", sep = "/"))
data <- acc_table_whole
title <- "A. All individual maps"
ggplot(data) +
  ggtitle(title) +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "point", size = 1, fun.y = mean, color = red) +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "point", size = 1, fun.y = mean, color = "lightskyblue3") +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "line", fun.y = mean, color = red, alpha = 0.6, linetype = "dashed") +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "line", fun.y = mean, color = "lightskyblue3", alpha = 0.6) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_concepts_mean - acc_concepts_sd, ymax = acc_concepts_mean + acc_concepts_sd, alpha = 0.2, fill = red)) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_non_duplicated_mean - acc_non_duplicated_sd, ymax = acc_non_duplicated_mean + acc_non_duplicated_sd, alpha = 0.2, fill = "lightskyblue3")) +
  xlab("Number of maps") +
  ylab("Number of concepts") +
  scale_fill_manual(values = c(red, green), name="", labels=c("Accumulated concepts", "Unique concepts")) +
  scale_alpha(NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")

# acc_table_researchers <- read.csv(paste(di, output_folder, "3.2.1 acc_table_researchers.csv", sep = "/"))
# data <- acc_table_researchers
# title <- "D. Researchers individual maps"
# ggplot(data) +
#   ggtitle(title) +
#   stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "point", size = 1, fun.y = mean, color = red) +
#   stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "point", size = 1, fun.y = mean, color = "lightskyblue3") +
#   stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "line", fun.y = mean, color = red, alpha = 0.6, linetype = "dashed") +
#   stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "line", fun.y = mean, color = "lightskyblue3", alpha = 0.6) +
#   geom_ribbon(aes(x = matrix_nr, ymin = acc_concepts_mean - acc_concepts_sd, ymax = acc_concepts_mean + acc_concepts_sd, alpha = 0.2, fill = red)) +
#   geom_ribbon(aes(x = matrix_nr, ymin = acc_non_duplicated_mean - acc_non_duplicated_sd, ymax = acc_non_duplicated_mean + acc_non_duplicated_sd, alpha = 0.2, fill = "lightskyblue3")) +
#   xlab("Number of maps") +
#   ylab("Number of concepts") +
#   scale_fill_manual(values = c(red, green), name="", labels=c("Accumulated concepts", "Unique concepts")) +
#   scale_alpha(NULL) +
#   theme_minimal() +
#   theme(legend.position = "bottom")
# 
# acc_table_forestry <- read.csv(paste(di, output_folder, "3.2.2 acc_table_forestry.csv", sep = "/"))
# data <- acc_table_forestry
# title <- "B. Forestry managers individual maps"
# ggplot(data) +
#   ggtitle(title) +
#   stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "point", size = 1, fun.y = mean, color = red) +
#   stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "point", size = 1, fun.y = mean, color = "lightskyblue3") +
#   stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "line", fun.y = mean, color = red, alpha = 0.6, linetype = "dashed") +
#   stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "line", fun.y = mean, color = "lightskyblue3", alpha = 0.6) +
#   geom_ribbon(aes(x = matrix_nr, ymin = acc_concepts_mean - acc_concepts_sd, ymax = acc_concepts_mean + acc_concepts_sd, alpha = 0.2, fill = red)) +
#   geom_ribbon(aes(x = matrix_nr, ymin = acc_non_duplicated_mean - acc_non_duplicated_sd, ymax = acc_non_duplicated_mean + acc_non_duplicated_sd, alpha = 0.2, fill = "lightskyblue3")) +
#   xlab("Number of maps") +
#   ylab("Number of concepts") +
#   scale_fill_manual(values = c(red, green), name="", labels=c("Accumulated concepts", "Unique concepts")) +
#   scale_alpha(NULL) +
#   theme_minimal() +
#   theme(legend.position = "bottom")
# 
# acc_table_key_stakeholders <- read.csv(paste(di, output_folder, "3.2.3 acc_table_key_stakeholders.csv", sep = "/"))
# data <- acc_table_key_stakeholders
# title <- "C. Key stakeholders individual maps"
# ggplot(data) +
#   ggtitle(title) +
#   stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "point", size = 1, fun.y = mean, color = red) +
#   stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "point", size = 1, fun.y = mean, color = "lightskyblue3") +
#   stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "line", fun.y = mean, color = red, alpha = 0.6, linetype = "dashed") +
#   stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "line", fun.y = mean, color = "lightskyblue3", alpha = 0.6) +
#   geom_ribbon(aes(x = matrix_nr, ymin = acc_concepts_mean - acc_concepts_sd, ymax = acc_concepts_mean + acc_concepts_sd, alpha = 0.2, fill = red)) +
#   geom_ribbon(aes(x = matrix_nr, ymin = acc_non_duplicated_mean - acc_non_duplicated_sd, ymax = acc_non_duplicated_mean + acc_non_duplicated_sd, alpha = 0.2, fill = "lightskyblue3")) +
#   xlab("Number of maps") +
#   ylab("Number of concepts") +
#   scale_fill_manual(values = c(red, green), name="", labels=c("Accumulated concepts", "Unique concepts")) +
#   scale_alpha(NULL) +
#   scale_x_continuous(breaks = c(0, 5, 10), limits = c(0,10))+
#   theme_minimal() +
#   theme(legend.position = "bottom")
```

# Figure_inout_concepts - not distinguishing in and out degree

Whole community
```{r}
per_group_concept_indices <- read.csv(paste(di, output_folder, "8.2 per_group_concept_indices.csv", sep = "/"), sep = ";")

n <- 10 
title <- "A. Social map"

filt_degrees <- per_group_concept_indices %>%
  select(Concept, Centrality_agg) %>%
  top_n(n, Centrality_agg) %>%
  mutate(Centrality = Centrality_agg) %>%
  select(Concept, Centrality)
filt_melted <- melt(filt_degrees, id.vars=c("Concept"))
colnames(filt_melted) <- c("Concept", "Variable", "Centrality")
filt_melted <- within(filt_melted, {
  Concept <- factor(Concept, levels = names(sort(tapply(Centrality, Concept, sum))))
})

ggplot(filt_melted, aes(x= Concept, y = Centrality, fill = Variable)) +
  scale_fill_manual(values = c(green, red)) +
  geom_bar(stat = "identity") +
  ggtitle(title) +
  coord_flip() +
  theme_minimal() +
  theme(axis.text.x = element_text(), legend.position = "bottom")
```

# Figure_inout_concepts - not distinguishing in and out degree and all concepts in all groups

```{r}
per_group_concept_indices <- read.csv(paste(di, input_folder, "8.2 filtered_top_10_across_communities.csv", sep = "/"), sep = ";", dec = ",")
per_group_concept_indices[is.na(per_group_concept_indices) == TRUE] <- 0
```

Socio-economic agents'
```{r}
title <- "Socio-economic agents' map"

filt_degrees <- per_group_concept_indices %>%
  select(Concept, Centrality_O)
filt_melted <- melt(filt_degrees, id.vars=c("Concept"))
colnames(filt_melted) <- c("Concept", "Variable", "Centrality")
filt_melted <- within(filt_melted, {
  Concept <- factor(Concept, levels = names(sort(tapply(Centrality, Concept, sum))))
})

ggplot(filt_melted, aes(x= Concept, y = Centrality, fill = Variable)) +
  scale_fill_manual(values = c(green, red)) +
  geom_bar(stat = "identity") +
  ggtitle(title) +
  coord_flip() +
  theme_minimal() +
  theme(axis.text.x = element_text(), legend.position = "bottom") +
  ylim(0, 35)
```

Researchers'
```{r}
title <- "Researchers' map"

filt_degrees <- per_group_concept_indices %>%
  select(Concept, Centrality_R)
filt_melted <- melt(filt_degrees, id.vars=c("Concept"))
colnames(filt_melted) <- c("Concept", "Variable", "Centrality")
filt_melted <- within(filt_melted, {
  Concept <- factor(Concept, levels = names(sort(tapply(Centrality, Concept, sum))))
})

ggplot(filt_melted, aes(x= Concept, y = Centrality, fill = Variable)) +
  scale_fill_manual(values = c(green, red)) +
  geom_bar(stat = "identity") +
  ggtitle(title) +
  coord_flip() +
  theme_minimal() +
  theme(axis.text.x = element_text(), legend.position = "bottom") +
  ylim(0, 35)
```

Forestry managers'
```{r}
title <- "Forestry managers' map"

filt_degrees <- per_group_concept_indices %>%
  select(Concept, Centrality_FM)
filt_melted <- melt(filt_degrees, id.vars=c("Concept"))
colnames(filt_melted) <- c("Concept", "Variable", "Centrality")
filt_melted <- within(filt_melted, {
  Concept <- factor(Concept, levels = names(sort(tapply(Centrality, Concept, sum))))
})

ggplot(filt_melted, aes(x= Concept, y = Centrality, fill = Variable)) +
  scale_fill_manual(values = c(green, red)) +
  geom_bar(stat = "identity") +
  ggtitle(title) +
  coord_flip() +
  theme_minimal() +
  theme(axis.text.x = element_text(), legend.position = "bottom") +
  ylim(0, 35)
```

# Figure_relations_occurrence_histogram

```{r}
occ_melted <- read.csv(paste(di, output_folder, "5.0 occ_melted.csv", sep = "/"))

ggplot(occ_melted, aes(x = occurrences, y = value)) +
  geom_col(fill = green) +
  theme_minimal() +
  xlab("What number of times") +
  ylab("How many relationships happened")
```

# [Figure_community_map]

Manual

# Figure_per_group_classification

```{r}
# Load data
whole_group <- read.csv(paste(di, output_folder, "5.4 dpsir_concept_classification.csv", sep = "/"), sep = ";")
per_group <- read.csv(paste(di, output_folder, "8.3 per_group_dpsir_classification.csv", sep = "/"), sep = ";")

all_data <- left_join(whole_group, per_group) %>%
  mutate(Whole_community = percentage_classes,
         Researchers = res_percentage_dpsir_classes,
         Forest_managers = man_percentage_dpsir_classes,
         Key_stakeholders = other_percentage_dpsir_classes) %>%
  select(DPSIR, Whole_community, Researchers, Forest_managers, Key_stakeholders) %>%
  mutate(DPSIR_alphabetic = as.character(c("E", "B", "D", "A", "C")))

all_data <- all_data[,-1]
all_data <- all_data[order(all_data$DPSIR_alphabetic),]
rownames(all_data) <- all_data[,5]
all_data <- as.data.frame(t(as.matrix(all_data[,c(1:4)])))
# all_data$Stakeholder <- rownames(all_data)
all_data$Stakeholder <- c("Social map", "Researchers' community map", "Forest managers' community map", "Key stakeholders' community map")
```

# Figure_per_group_classification - all comm. maps, no social map

```{r}
# Load data
all_data <- left_join(whole_group, per_group) %>%
  mutate(Whole_community = percentage_classes,
         Researchers = res_percentage_dpsir_classes,
         Forest_managers = man_percentage_dpsir_classes,
         Key_stakeholders = other_percentage_dpsir_classes) %>%
  select(DPSIR, Researchers, Forest_managers, Key_stakeholders) %>%
  mutate(DPSIR_alphabetic = as.character(c("E", "B", "D", "A", "C")))

all_data <- all_data[,-1]
all_data <- all_data[order(all_data$DPSIR_alphabetic),]
rownames(all_data) <- all_data[,4]
all_data <- as.data.frame(t(as.matrix(all_data[,c(1:3)])))
# all_data$Stakeholder <- rownames(all_data)
all_data$Stakeholder <- c("Researchers' community map", "Forest managers' community map", "Key stakeholders' community map")

all_data %>% 
     ggparcoord(
         columns = 1:5, groupColumn = 6, order = c("allClass"),
         scale = "globalminmax",
         showPoints = TRUE,
         alphaLines = 0.3) +
  scale_color_manual(values = c("Researchers' community map" = green, "Forest managers' community map" = blue, "Key stakeholders' community map" = orange)) +
  coord_flip() +
  theme_minimal() +
  theme() +
  ylab("Percentage (%)") +
  xlab(NULL)
```

# [Figure_implications]