---
title: "Analysis of homogenised individual maps"
output:
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

input files: csv files containing the matrices resulting from the FCM interviews, homogenised and without empty concepts ("-").

```{r include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages
library(FCMapper)
library("rlist")
library(dplyr)
library(ggplot2)
library(reshape)
library(knitr)

# Directory
di <- "/Users/maria.suarez.munoz/Google Drive/ms_FuzzyCognitiveMapping/FCM_analysis" # Mac

matrices_folder <- "/input_files/homogenised_matrices/"
input_folder <- "/input_files/"

files <- list.files(paste(di, matrices_folder, sep = "/"), pattern = "*.csv")

gephi_output_folder <- "/output_files/files_for_Gephi_plotting/aggregated/"

output_folder <- "/output_files/"
```

```{r, include=FALSE}
# Build maps list
matrices_list <- list()

for (i in 1:length(files)) {
  my_matrix <- read.csv(paste(di, matrices_folder, files[i], sep = ""), sep = ";", na.strings=c("","NA"), dec = ",")
  assign('concept_labels', as.character(my_matrix[,1])) # extract concept names
  my_matrix <- my_matrix[,-1] # discard first column for matrix (concept names)
  colnames(my_matrix) <- concept_labels # to avoid spaces being replaced by dots
  
  matrices_list <- list.append(matrices_list, my_matrix)
}
```

Checking
```{r}
ifelse(i == 41,
       "everything alright",
       "ERROR in files loading")
```

# Basic accumulation curve

Duplicated concepts within a matrix are considered the same, although originally (i.e. in the original matrices) they were different!

```{r}
acc_table <- data.frame(matrix_nr = integer(),
                        nr_concepts_in_matrix = integer(),
                        acc_concepts = integer(),
                        acc_non_duplicated = integer()) # empty data frame

all_concepts_vector <- c()
unique_concepts_vector <- c()

for (i in 1:length(matrices_list)) {
# for (i in 1:6) { # for testing
  matrix_nr <- i
  concepts_in_matrix <- unique(colnames(matrices_list[[i]])) # if duplicated concepts considered, eliminate unique
  nr_concepts_in_matrix <- length(concepts_in_matrix)
  
  all_concepts_vector <- c(all_concepts_vector, concepts_in_matrix)
  nr_all_concepts <- length(all_concepts_vector)
  
  unique_concepts_vector <- unique(all_concepts_vector)
  nr_unique_concepts <- length(unique_concepts_vector)
  
  acc_table <- rbind(acc_table, data.frame(matrix_nr = i,
                        nr_concepts_in_matrix = nr_concepts_in_matrix,
                        acc_concepts = nr_all_concepts,
                        acc_non_duplicated = nr_unique_concepts))
  
}

ggplot(acc_table) +
  geom_point(aes(x = matrix_nr, y = acc_concepts), color = "red") +
  geom_point(aes(x = matrix_nr, y = acc_non_duplicated), color = "blue") +
  theme_minimal() +
  xlab("Map number") +
  ylab("Number of concepts") +
  ggtitle("Accumulation curve")
```

# Improved accumulation curve

Accumulation curve data are calculated altering the matrices ordering, in order to unbias the accumulation

Duplicated concepts within a matrix are considered the same, although originally (i.e. in the original matrices) they were different!

```{r}
acc_table_iterations <- data.frame(matrix_nr = integer(),
                        acc_concepts = integer(),
                        acc_non_duplicated = integer()) # empty data frame

nr_iterations <- 1000

for (j in 1:nr_iterations) {
  matrix_order <- sample(1:length(matrices_list), length(matrices_list), replace = FALSE)
  all_concepts_vector <- c()
  unique_concepts_vector <- c()
  
  for (i in 1:length(matrices_list)) {
    matrix_nr <- i
    concepts_in_matrix <- unique(colnames(matrices_list[[matrix_order[i]]]))
    all_concepts_vector <- c(all_concepts_vector, concepts_in_matrix)
    nr_all_concepts <- length(all_concepts_vector)
    unique_concepts_vector <- unique(all_concepts_vector)
    nr_unique_concepts <- length(unique_concepts_vector)
    acc_table_iterations <- rbind(acc_table_iterations, data.frame(matrix_nr = i, acc_concepts = nr_all_concepts, acc_non_duplicated = nr_unique_concepts))
  }
}
```

```{r}
acc_table_iterations_summary <- acc_table_iterations %>%
  group_by(matrix_nr) %>%
  summarise(acc_concepts_mean = mean(acc_concepts),
            acc_concepts_sd = sd(acc_concepts),
            acc_non_duplicated_mean = mean(acc_non_duplicated),
            acc_non_duplicated_sd = sd(acc_non_duplicated))

write.csv(acc_table_iterations_summary, paste(di, output_folder, "3.0 acc_table_whole_community.csv", sep = ""))
```

```{r}
title <- paste("Accumulation curve for ", nr_iterations, " iterations", sep = "")

ggplot(acc_table_iterations_summary) +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "point", size = 0.2, fun.y = mean, color = "indianred4") +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "point", size = 0.2, fun.y = mean, color = "lightskyblue3") +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "line", fun.y = mean, color = "indianred4", alpha = 0.6) +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "line", fun.y = mean, color = "lightskyblue3", alpha = 0.6) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_concepts_mean - acc_concepts_sd, ymax = acc_concepts_mean + acc_concepts_sd, alpha = 0.2, fill = "indianred4")) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_non_duplicated_mean - acc_non_duplicated_sd, ymax = acc_non_duplicated_mean + acc_non_duplicated_sd, alpha = 0.2, fill = "lightskyblue3")) +
  theme(legend.position = "bottom") +
  xlab("Map number") +
  ylab("Number of concepts") +
  ggtitle("Accumulation curve") +
  scale_fill_manual(values=c("indianred4", "lightskyblue3"), name="", labels=c("Accumulated concepts", "Unique concepts")) +
  scale_alpha(name = "", labels = "") +
  ggtitle(title)
```
  
# Maps comparison differentiating among groups

Load stakeholders table
```{r}
ref_table <- read.csv(paste(di, output_folder, "1.0. maps_to_matrices_ref_table.csv", sep = ""), sep = ";", na.strings=c("","NA"), dec = ",")

ref_table$Type <- substring(ref_table$Stakeholders_type, 1, 1)
ref_table$typenr <- c()
  
for (i in 1:length(ref_table$Matrix_nr)) {
  ifelse(ref_table$Matrix_nr[i] < 10,
         index <- paste("0", ref_table$Matrix_nr[i], sep = ""),
         index <- ref_table$Matrix_nr[i])
  ref_table$typenr[i] <- paste(ref_table$Type[i], index, sep = "_")
}
```

Calculate comparison indexes
```{r, echo=FALSE}
# create table to store comparisons
other_vector <- c()
for (i in 1:length(files)) {
  name <- ref_table$typenr[i]
  other_vector <- c(other_vector, name) 
}

jaccard_per_comparison <- matrix(NA, nrow = length(files), ncol = length(files), dimnames = list(other_vector, other_vector))
# S2_per_comparison <- matrix(NA, nrow = length(files), ncol = length(files), dimnames = list(other_vector, other_vector))

# fill in tables
for (i in 1:length(files)) {
  for (j in 1:length(files)){
    a <- comp.maps(colnames(matrices_list[i][[1]]), colnames(matrices_list[j][[1]]))
    jaccard_per_comparison[i,j] <- a$Jaccard
    #S2_per_comparison[i,j] <- a$S2
  }
}
``` 

Fetch Jaccard data and create levels
```{r}
jaccard_per_comparison_ordered <- jaccard_per_comparison[order(as.factor(row.names(jaccard_per_comparison))),]
jaccard_per_comparison_transposed <- t(jaccard_per_comparison_ordered)
jaccard_per_comparison_reordered <- jaccard_per_comparison_transposed[order(as.factor(row.names(jaccard_per_comparison_transposed))),]
jaccard_per_comparison_reordered[upper.tri(jaccard_per_comparison_reordered, diag = FALSE)] <- NA
jaccard_per_melted <- melt(jaccard_per_comparison_reordered)
jaccard_per_melted <- jaccard_per_melted %>%
  filter(is.na(value) == FALSE)

jaccard_per_melted$Level <- c()
for (i in 1:length(jaccard_per_melted$value)) {
  ifelse(jaccard_per_melted$value[i] > 0.75,
         jaccard_per_melted$Level[i] <- "High",
         ifelse(jaccard_per_melted$value[i] < 0.25,
                jaccard_per_melted$Level[i] <- "Very low",
                ifelse(jaccard_per_melted$value[i] > 0.5,
                       jaccard_per_melted$Level[i] <- "Medium",
                       jaccard_per_melted$Level[i] <- "Low")))
}
jaccard_levels <- jaccard_per_melted %>%
  select(X1, X2, Level)
```

Jaccard plot
```{r}
cols <- c("Very low" = "lightskyblue3", "Low" = "orange2", "High" = "indianred4")
ggplot() +
  geom_tile(data = jaccard_levels, aes(x = X1, y = X2, fill = Level)) +
  xlab("") +
  ylab("") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6),
        axis.text.y = element_text(size = 6)) +
  scale_colour_manual(values = cols,
                      aesthetics = c("colour", "fill")) +
  ggtitle("Jaccard index comparison")
```

Fetch S2 data and create levels
```{r}
# S2_per_comparison_ordered <- S2_per_comparison[order(as.factor(row.names(S2_per_comparison))),]
# S2_per_comparison_transposed <- t(S2_per_comparison_ordered)
# S2_per_comparison_reordered <- S2_per_comparison_transposed[order(as.factor(row.names(S2_per_comparison_transposed))),]
# S2_per_comparison_reordered[upper.tri(S2_per_comparison_reordered, diag = FALSE)] <- NA
# S2_per_melted <- melt(S2_per_comparison_reordered)
# S2_per_melted <- S2_per_melted %>%
#   filter(is.na(value) == FALSE)
# 
# S2_per_melted$level <- c()
# for (i in 1:length(S2_per_melted$value)) {
#   ifelse(S2_per_melted$value[i] <0.25,
#          S2_per_melted$level[i] <- "low",
#          ifelse(S2_per_melted$value[i] > 0.5,
#                 S2_per_melted$level[i] <- "TOO SIMILAR",
#                 S2_per_melted$level[i] <- "high"))
# }
# S2_levels <- S2_per_melted %>%
#   select(X1, X2, level)
```

S2 plot
```{r}
# cols <- c("low" = "lightskyblue3", "high" = "indianred4", "TOO SIMILAR" = "red")
# ggplot() +
#   geom_tile(data = S2_levels, aes(x = X1, y = X2, fill = level)) +
#   xlab("Matrices") +
#   ylab("Matrices") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   scale_colour_manual(values = cols,
#                       aesthetics = c("colour", "fill"))
```
  
# Matrices indices

All homogenised maps indices

```{r, echo = FALSE}
homogenised_matrices_indices <- data.frame(Index = c("Nr_connections", "Connection_density", "Nr_concepts", "Nr_transmitters", "Nr_receivers", "Nr_no_connections", "Nr_ordinary", "Nr_self_loops", "Connections_variable", "Complexity", "Hierarchy", "Density_with_loops", "Percentage_T", "Percentage_R", "Percentage_O"))
  
for (i in 1:length(matrices_list)) {
  a_matrix <- matrices_list[[i]]
  a_matrix[is.na(a_matrix)] <- 0
  matrix_indexes <- matrix.indices(a_matrix)
  D_self <- as.numeric(matrix_indexes$Value[1]) / as.numeric(matrix_indexes$Value[3])^2
  Percentage_T <- as.numeric(matrix_indexes$Value[4]) * 100 / as.numeric(matrix_indexes$Value[3])
  Percentage_R <- as.numeric(matrix_indexes$Value[5]) * 100 / as.numeric(matrix_indexes$Value[3])
  Percentage_O <- as.numeric(matrix_indexes$Value[7]) * 100 / as.numeric(matrix_indexes$Value[3])
  
  matrix_indexes$Index <- as.character(matrix_indexes$Index)
  matrix_indexes <- rbind(matrix_indexes, c("Density with loops", D_self))
  matrix_indexes <- rbind(matrix_indexes, c("Percentage_T", Percentage_T))
  matrix_indexes <- rbind(matrix_indexes, c("Percentage_R", Percentage_R))
  matrix_indexes <- rbind(matrix_indexes, c("Percentage_O", Percentage_O))
  
  matrix_indexes$Index <- as.factor(matrix_indexes$Index)
  matrix_indexes$Value <- as.numeric(matrix_indexes$Value)

  matrix_indexes <- matrix_indexes %>%
    select(Value)
  colnames(matrix_indexes) <- paste("matrix_", i, sep = "")
  homogenised_matrices_indices <- cbind(homogenised_matrices_indices, matrix_indexes)
}

column_names <- homogenised_matrices_indices$Index

homogenised_matrices_indices <- homogenised_matrices_indices[,2:length(homogenised_matrices_indices)]
homogenised_matrices_indices <- as.matrix(t(homogenised_matrices_indices))
colnames(homogenised_matrices_indices) <- column_names
homogenised_matrices_indices <- as.data.frame(homogenised_matrices_indices)

homogenised_matrices_indices$Stakeholder_type <- ref_table$Type
homogenised_matrices_indices <- homogenised_matrices_indices[with(homogenised_matrices_indices, order(Stakeholder_type)), ]
```

# Statistical comparison among groups

```{r}
boxplot(homogenised_matrices_indices$Nr_concepts ~ homogenised_matrices_indices$Stakeholder_type)

model_Nr_concepts <- aov(Nr_concepts ~ Stakeholder_type, data = homogenised_matrices_indices)
plot(model_Nr_concepts)
shapiro.test(residuals(model_Nr_concepts)) # Normal
summary(model_Nr_concepts) # means cannot be said different
TukeyHSD(model_Nr_concepts) # means cannot be said different
```

```{r}
boxplot(homogenised_matrices_indices$Percentage_T ~ homogenised_matrices_indices$Stakeholder_type)

model_Percentage_T <- aov(Percentage_T ~ Stakeholder_type, data = homogenised_matrices_indices)
plot(model_Percentage_T)
shapiro.test(residuals(model_Percentage_T)) # Normal
summary(model_Percentage_T) # means cannot be said different
TukeyHSD(model_Percentage_T) # means cannot be said different
```

```{r}
boxplot(homogenised_matrices_indices$Percentage_R ~ homogenised_matrices_indices$Stakeholder_type)

model_Percentage_R <- aov(Percentage_R ~ Stakeholder_type, data = homogenised_matrices_indices)
plot(model_Percentage_R)
shapiro.test(residuals(model_Percentage_R)) # Normal
summary(model_Percentage_R) # means cannot be said different
TukeyHSD(model_Percentage_R) # means cannot be said different
```

```{r}
boxplot(homogenised_matrices_indices$Percentage_O ~ homogenised_matrices_indices$Stakeholder_type)

model_Percentage_O <- aov(Percentage_O ~ Stakeholder_type, data = homogenised_matrices_indices)
plot(model_Percentage_O)
shapiro.test(residuals(model_Percentage_O)) # Normal
summary(model_Percentage_O) # means cannot be said different
TukeyHSD(model_Percentage_O) # means cannot be said different
```

```{r}
boxplot(homogenised_matrices_indices$Complexity ~ homogenised_matrices_indices$Stakeholder_type)

model_Complexity <- aov(Complexity ~ Stakeholder_type, data = homogenised_matrices_indices)
plot(model_Complexity)
shapiro.test(residuals(model_Complexity)) # not normally distributed
hist(homogenised_matrices_indices$Complexity)
leveneTest(Complexity ~ Stakeholder_type, data = homogenised_matrices_indices) # homocedastic

Complexity_log <- log(homogenised_matrices_indices$Complexity)
model_Complexity_log <- aov(Complexity_log ~ homogenised_matrices_indices$Stakeholder_type)
shapiro.test(residuals(model_Complexity_log)) # Normales
summary(model_Complexity_log) # means cannot be said different
TukeyHSD(model_Complexity_log) # means cannot be said different
```

```{r}
boxplot(homogenised_matrices_indices$Nr_connections ~ homogenised_matrices_indices$Stakeholder_type)

model_Nr_connections <- aov(Nr_connections ~ Stakeholder_type, data = homogenised_matrices_indices)
plot(model_Nr_connections)
shapiro.test(residuals(model_Nr_connections)) # not normally distributed
hist(homogenised_matrices_indices$Nr_connections)
leveneTest(Nr_connections ~ Stakeholder_type, data = homogenised_matrices_indices) # homocedastic

Nr_connections_log <- log(homogenised_matrices_indices$Nr_connections)

model_Nr_connections_log <- aov(Nr_connections_log ~ homogenised_matrices_indices$Stakeholder_type)
shapiro.test(residuals(model_Nr_connections_log)) # Normal

summary(model_Nr_connections_log) # means cannot be said different
TukeyHSD(model_Nr_connections_log) # means cannot be said different
```

```{r}
boxplot(homogenised_matrices_indices$Connections_variable ~ homogenised_matrices_indices$Stakeholder_type)

model_Connections_variable <- aov(Connections_variable ~ Stakeholder_type, data = homogenised_matrices_indices)
plot(model_Connections_variable)
shapiro.test(residuals(model_Connections_variable)) # not normally distributed

Connections_variable_log <- log(homogenised_matrices_indices$Connections_variable)
model_Connections_variable_log <- aov(Connections_variable_log ~ homogenised_matrices_indices$Stakeholder_type)
shapiro.test(residuals(model_Connections_variable_log)) # Not normal

Connections_variable_asin <- asin(homogenised_matrices_indices$Connections_variable)
model_Connections_variable_asin <- aov(Connections_variable_asin ~ homogenised_matrices_indices$Stakeholder_type)
shapiro.test(residuals(model_Connections_variable_asin)) # Not normal
```

```{r}
boxplot(homogenised_matrices_indices$Density_with_loops ~ homogenised_matrices_indices$Stakeholder_type)

model_Density_with_loops <- aov(Density_with_loops ~ Stakeholder_type, data = homogenised_matrices_indices)
plot(model_Density_with_loops)
shapiro.test(residuals(model_Density_with_loops)) # not normally distributed

Density_log <- log(homogenised_matrices_indices$Density_with_loops)

model_Density_log <- aov(Density_log ~ homogenised_matrices_indices$Stakeholder_type)
shapiro.test(residuals(model_Density_log))

hist(Density_log)
summary(model_Density_log) # means cannot be said different
TukeyHSD(model_Density_log) # means cannot be said different
```

# Summary table

```{r, include=FALSE}
homogenised_matrices_indices_notype <- homogenised_matrices_indices[,1:15]

mean_tb <- summarise_all(homogenised_matrices_indices_notype, mean)
sd_tb <- summarise_all(homogenised_matrices_indices_notype, sd)
min_tb <- summarise_all(homogenised_matrices_indices_notype, min)
max_tb <- summarise_all(homogenised_matrices_indices_notype, max)

summary_tb <- rbind(mean_tb, sd_tb, min_tb, max_tb)
rownames(summary_tb) <- c("Mean_all", "SD_all", "Minimum_all", "Maximum_all")

summary_tb$Stakeholder_type <- NA
homogenised_matrices_indices <- rbind(homogenised_matrices_indices, summary_tb)
```

Export indices table

```{r}
write.table(homogenised_matrices_indices, paste(di, output_folder, "3.1 homogenised_matrices_indices.csv", sep = ""), sep = ";", row.names = TRUE)
```

**Note on density**

Connection density = Number of connections / Number of concepts

Density as [@Ozesmi2004]: Number of connections / Number of possible connections
  with self loops: Number of connections / (Number of concepts^2)
  without self loops: Number of connections / (Number of concepts * (Number of concepts - 1))
  
We consider that self-loops are possible, and add this index in the table ("Density with loops")

```{r, echo = FALSE}
# D_noself <- as.numeric(meanmatrix_indices$Value[1]) / (as.numeric(meanmatrix_indices$Value[3])*(as.numeric(matrix_indices$Value[3]) - 1)) # in case self-loops are not allowed in the map - not our case
```

Summary tables per group
```{r}
# Other stakeholders
others_indices <- homogenised_matrices_indices %>% filter(Stakeholder_type == "S")
others_indices <- others_indices[,1:15]
mean_tb <- summarise_all(others_indices, mean)
sd_tb <- summarise_all(others_indices, sd)
min_tb <- summarise_all(others_indices, min)
max_tb <- summarise_all(others_indices, max)
summary_others <- rbind(mean_tb, sd_tb, min_tb, max_tb)
rownames(summary_others) <- c("Mean_socio-economic_agents", "SD_socio-economic_agents", "Minimum_socio-economic_agents", "Maximum_socio-economic_agents")

# Forestry managers
managers_indices <- homogenised_matrices_indices %>%
  filter(Stakeholder_type == "F")
managers_indices <- managers_indices[,1:15]
mean_tb <- summarise_all(managers_indices, mean)
sd_tb <- summarise_all(managers_indices, sd)
min_tb <- summarise_all(managers_indices, min)
max_tb <- summarise_all(managers_indices, max)
summary_managers <- rbind(mean_tb, sd_tb, min_tb, max_tb)
rownames(summary_managers) <- c("Mean_managers", "SD_managers", "Minimum_managers", "Maximum_managers")

# Researchers
researchers_indices <- homogenised_matrices_indices %>%
  filter(Stakeholder_type == "R")
researchers_indices <- researchers_indices[,1:15]
mean_tb <- summarise_all(researchers_indices, mean)
sd_tb <- summarise_all(researchers_indices, sd)
min_tb <- summarise_all(researchers_indices, min)
max_tb <- summarise_all(researchers_indices, max)
summary_researchers <- rbind(mean_tb, sd_tb, min_tb, max_tb)
rownames(summary_researchers) <- c("Mean_researchers", "SD_researchers", "Minimum_researchers", "Maximum_researchers")

per_group_summary <- rbind(summary_others, summary_managers)
per_group_summary <- rbind(per_group_summary, summary_researchers)
```

```{r}
write.table(per_group_summary, paste(di, output_folder, "3.2. per_group_summary_indices_homogenised.csv", sep = ""), sep = ";", row.names = TRUE)
```
