---
title: "3.2 per-group accumulation curves"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages
library(FCMapper)
library("rlist")
library(dplyr)
library(ggplot2)
library(reshape)
library(knitr)

# Directory
di <- "/Users/maria.suarez.munoz/Google Drive/ms_FuzzyCognitiveMapping/FCM_analysis" # Mac

input_folder <- "input_files"

files <- list.files(paste(di, input_folder, "homogenised_matrices", sep = "/"), pattern = "*.csv")

output_folder <- "/output_files/"
```

```{r, include=FALSE}
# Build maps list
matrices_list <- list()

for (i in 1:length(files)) {
  my_matrix <- read.csv(paste(di, input_folder, "homogenised_matrices", files [i], sep = "/"), sep = ";", na.strings=c("","NA"), dec = ",")
  assign('concept_labels', as.character(my_matrix[,1])) # extract concept names
  my_matrix <- my_matrix[,-1] # discard first column for matrix (concept names)
  colnames(my_matrix) <- concept_labels # to avoid spaces being replaced by dots
  
  matrices_list <- list.append(matrices_list, my_matrix)
}

# Checking
ifelse(i == 41,
       "everything alright",
       "ERROR in files loading")
```

Load stakeholders table
```{r}
ref_table <- read.csv(paste(di, output_folder, "1.0. maps_to_matrices_ref_table.csv", sep = ""), sep = ";", na.strings=c("","NA"), dec = ",")

ref_table$Type <- substring(ref_table$Stakeholders_type, 1, 1)
ref_table$typenr <- c()
  
for (i in 1:length(ref_table$Matrix_nr)) {
  ifelse(ref_table$Matrix_nr[i] < 10,
         index <- paste("0", ref_table$Matrix_nr[i], sep = ""),
         index <- ref_table$Matrix_nr[i])
  ref_table$typenr[i] <- paste(ref_table$Type[i], index, sep = "_")
}
```

Build list of maps per stakeholder group
```{r}
researchers <- c()
forestry_managers <- c()
others <- c()

for (i in 1:length(ref_table$Entrevista)) {
  ifelse(ref_table$Stakeholders_type[i] == "Researchers",
         researchers <- c(researchers, i),
         ifelse(ref_table$Stakeholders_type[i] == "Forestry managers",
                forestry_managers <- c(forestry_managers, i),
                others <- c(others, i)))
}

researchers_list <- list()
for (i in 1:length(researchers)) {
  my_matrix <- read.csv(paste(di, input_folder, "homogenised_matrices", files[researchers[i]], sep = "/"), sep = ";", na.strings=c("","NA"), dec = ",")
  assign('concept_labels', as.character(my_matrix[,1])) # extract concept names
  my_matrix <- my_matrix[,-1] # discard first column for matrix (concept names)
  colnames(my_matrix) <- concept_labels # to avoid spaces being replaced by dots
  researchers_list <- list.append(researchers_list, my_matrix)
}

managers_list <- list()
for (i in 1:length(forestry_managers)) {
  my_matrix <- read.csv(paste(di, input_folder, "homogenised_matrices", files[forestry_managers[i]], sep = "/"), sep = ";", na.strings=c("","NA"), dec = ",")
  assign('concept_labels', as.character(my_matrix[,1])) # extract concept names
  my_matrix <- my_matrix[,-1] # discard first column for matrix (concept names)
  colnames(my_matrix) <- concept_labels # to avoid spaces being replaced by dots
  managers_list <- list.append(managers_list, my_matrix)
}

others_list <- list()
for (i in 1:length(others)) {
  my_matrix <- read.csv(paste(di, input_folder, "homogenised_matrices", files[others[i]], sep = "/"), sep = ";", na.strings=c("","NA"), dec = ",")
  assign('concept_labels', as.character(my_matrix[,1])) # extract concept names
  my_matrix <- my_matrix[,-1] # discard first column for matrix (concept names)
  colnames(my_matrix) <- concept_labels # to avoid spaces being replaced by dots
  others_list <- list.append(others_list, my_matrix)
}
```

# Researchers' accumulation curve

Accumulation curve data are calculated altering the matrices ordering, in order to unbias the accumulation

Duplicated concepts within a matrix are considered the same, although originally (i.e. in the original matrices) they were different!

```{r}
acc_table_iterations <- data.frame(matrix_nr = integer(),
                        acc_concepts = integer(),
                        acc_non_duplicated = integer()) # empty data frame

nr_iterations <- 1000

for (j in 1:nr_iterations) {
  matrix_order <- sample(1:length(researchers_list), length(researchers_list), replace = FALSE)
  all_concepts_vector <- c()
  unique_concepts_vector <- c()
  
  for (i in 1:length(researchers_list)) {
    matrix_nr <- i
    concepts_in_matrix <- unique(colnames(researchers_list[[matrix_order[i]]]))
    all_concepts_vector <- c(all_concepts_vector, concepts_in_matrix)
    nr_all_concepts <- length(all_concepts_vector)
    unique_concepts_vector <- unique(all_concepts_vector)
    nr_unique_concepts <- length(unique_concepts_vector)
    acc_table_iterations <- rbind(acc_table_iterations, data.frame(matrix_nr = i, acc_concepts = nr_all_concepts, acc_non_duplicated = nr_unique_concepts))
  }
}

acc_table_iterations_summary <- acc_table_iterations %>%
  group_by(matrix_nr) %>%
  summarise(acc_concepts_mean = mean(acc_concepts),
            acc_concepts_sd = sd(acc_concepts),
            acc_non_duplicated_mean = mean(acc_non_duplicated),
            acc_non_duplicated_sd = sd(acc_non_duplicated))

write.csv(acc_table_iterations_summary, paste(di, output_folder, "3.2.1 acc_table_researchers.csv", sep = ""))

title <- paste("Accumulation curve for researchers (", nr_iterations, " iterations)", sep = "")

ggplot(acc_table_iterations_summary) +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "point", size = 0.2, fun.y = mean, color = "indianred4") +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "point", size = 0.2, fun.y = mean, color = "lightskyblue3") +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "line", fun.y = mean, color = "indianred4", alpha = 0.6) +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "line", fun.y = mean, color = "lightskyblue3", alpha = 0.6) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_concepts_mean - acc_concepts_sd, ymax = acc_concepts_mean + acc_concepts_sd, alpha = 0.2, fill = "indianred4")) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_non_duplicated_mean - acc_non_duplicated_sd, ymax = acc_non_duplicated_mean + acc_non_duplicated_sd, alpha = 0.2, fill = "lightskyblue3")) +
  theme(legend.position = "none") +
  xlab("Map number") +
  ylab("Number of concepts") +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15)) +
  ggtitle("Accumulation curve") +
  scale_fill_manual(values=c("indianred4", "lightskyblue3"), name="", labels=c("Accumulated concepts", "Unique concepts")) +
  scale_alpha(name = "", labels = "") +
  ggtitle(title)
```

# Forestry managers' accumulation curve

Accumulation curve data are calculated altering the matrices ordering, in order to unbias the accumulation

Duplicated concepts within a matrix are considered the same, although originally (i.e. in the original matrices) they were different!

```{r}
acc_table_iterations <- data.frame(matrix_nr = integer(),
                        acc_concepts = integer(),
                        acc_non_duplicated = integer()) # empty data frame

nr_iterations <- 1000

for (j in 1:nr_iterations) {
  matrix_order <- sample(1:length(managers_list), length(managers_list), replace = FALSE)
  all_concepts_vector <- c()
  unique_concepts_vector <- c()
  
  for (i in 1:length(managers_list)) {
    matrix_nr <- i
    concepts_in_matrix <- unique(colnames(managers_list[[matrix_order[i]]]))
    all_concepts_vector <- c(all_concepts_vector, concepts_in_matrix)
    nr_all_concepts <- length(all_concepts_vector)
    unique_concepts_vector <- unique(all_concepts_vector)
    nr_unique_concepts <- length(unique_concepts_vector)
    acc_table_iterations <- rbind(acc_table_iterations, data.frame(matrix_nr = i, acc_concepts = nr_all_concepts, acc_non_duplicated = nr_unique_concepts))
  }
}

acc_table_iterations_summary <- acc_table_iterations %>%
  group_by(matrix_nr) %>%
  summarise(acc_concepts_mean = mean(acc_concepts),
            acc_concepts_sd = sd(acc_concepts),
            acc_non_duplicated_mean = mean(acc_non_duplicated),
            acc_non_duplicated_sd = sd(acc_non_duplicated))

write.csv(acc_table_iterations_summary, paste(di, output_folder, "3.2.2 acc_table_forestry.csv", sep = ""))

title <- paste("Accumulation curve for forestry managers (", nr_iterations, " iterations)", sep = "")

ggplot(acc_table_iterations_summary) +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "point", size = 0.2, fun.y = mean, color = "indianred4") +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "point", size = 0.2, fun.y = mean, color = "lightskyblue3") +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "line", fun.y = mean, color = "indianred4", alpha = 0.6) +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "line", fun.y = mean, color = "lightskyblue3", alpha = 0.6) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_concepts_mean - acc_concepts_sd, ymax = acc_concepts_mean + acc_concepts_sd, alpha = 0.2, fill = "indianred4")) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_non_duplicated_mean - acc_non_duplicated_sd, ymax = acc_non_duplicated_mean + acc_non_duplicated_sd, alpha = 0.2, fill = "lightskyblue3")) +
  theme(legend.position = "none") +
  xlab("Map number") +
  ylab("Number of concepts") +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)) +
  ggtitle("Accumulation curve") +
  scale_fill_manual(values=c("indianred4", "lightskyblue3"), name="", labels=c("Accumulated concepts", "Unique concepts")) +
  scale_alpha(name = "", labels = "") +
  ggtitle(title)
```

# Key stakeholders' accumulation curve

Accumulation curve data are calculated altering the matrices ordering, in order to unbias the accumulation

Duplicated concepts within a matrix are considered the same, although originally (i.e. in the original matrices) they were different!

```{r}
acc_table_iterations <- data.frame(matrix_nr = integer(),
                        acc_concepts = integer(),
                        acc_non_duplicated = integer()) # empty data frame

nr_iterations <- 1000

for (j in 1:nr_iterations) {
  matrix_order <- sample(1:length(others_list), length(others_list), replace = FALSE)
  all_concepts_vector <- c()
  unique_concepts_vector <- c()
  
  for (i in 1:length(others_list)) {
    matrix_nr <- i
    concepts_in_matrix <- unique(colnames(others_list[[matrix_order[i]]]))
    all_concepts_vector <- c(all_concepts_vector, concepts_in_matrix)
    nr_all_concepts <- length(all_concepts_vector)
    unique_concepts_vector <- unique(all_concepts_vector)
    nr_unique_concepts <- length(unique_concepts_vector)
    acc_table_iterations <- rbind(acc_table_iterations, data.frame(matrix_nr = i, acc_concepts = nr_all_concepts, acc_non_duplicated = nr_unique_concepts))
  }
}

acc_table_iterations_summary <- acc_table_iterations %>%
  group_by(matrix_nr) %>%
  summarise(acc_concepts_mean = mean(acc_concepts),
            acc_concepts_sd = sd(acc_concepts),
            acc_non_duplicated_mean = mean(acc_non_duplicated),
            acc_non_duplicated_sd = sd(acc_non_duplicated))

write.csv(acc_table_iterations_summary, paste(di, output_folder, "3.2.3 acc_table_key_stakeholders.csv", sep = ""))

title <- paste("Accumulation curve for other stakeholders (", nr_iterations, " iterations)", sep = "")

ggplot(acc_table_iterations_summary) +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "point", size = 0.2, fun.y = mean, color = "indianred4") +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "point", size = 0.2, fun.y = mean, color = "lightskyblue3") +
  stat_summary(aes(x = matrix_nr, y = acc_concepts_mean), geom = "line", fun.y = mean, color = "indianred4", alpha = 0.6) +
  stat_summary(aes(x = matrix_nr, y = acc_non_duplicated_mean), geom = "line", fun.y = mean, color = "lightskyblue3", alpha = 0.6) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_concepts_mean - acc_concepts_sd, ymax = acc_concepts_mean + acc_concepts_sd, alpha = 0.2, fill = "indianred4")) +
  geom_ribbon(aes(x = matrix_nr, ymin = acc_non_duplicated_mean - acc_non_duplicated_sd, ymax = acc_non_duplicated_mean + acc_non_duplicated_sd, alpha = 0.2, fill = "lightskyblue3")) +
  theme(legend.position = "none") +
  xlab("Map number") +
  ylab("Number of concepts") +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12)) +
  ggtitle("Accumulation curve") +
  scale_fill_manual(values=c("indianred4", "lightskyblue3"), name="", labels=c("Accumulated concepts", "Unique concepts")) +
  scale_alpha(name = "", labels = "") +
  ggtitle(title)
```