---
title: "Homogenised maps aggregation"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(dplyr)

di <- "/Users/maria.suarez.munoz/Google Drive/ms_FuzzyCognitiveMapping/FCM_analysis" # Mac

library(ggplot2)

homogenised_maps_folder <- "/input_files/homogenised_matrices/"
input_folder <- "/input_files/"
output_folder <- "/output_files/"
gephi_output_folder <- "/output_files/files_for_Gephi_plotting/aggregated/"

files <- list.files(paste(di, homogenised_maps_folder, sep = "/"), pattern = "*.csv")
```

Own method, other options: code from @Olazabal2016, and comb.maps function from FCMapper

- Generate all_concepts (vector with all the concepts in the maps, with repetitions) and all_relations (df with relationships from all maps)

```{r}
all_concepts <- c()
all_relations <- data.frame(matrix = integer(),
                            source_label = character(),
                            target_label = character(),
                            weight = numeric())

for (i in 1:length(files)) {
# for (i in 1:2) { # testing
  my_matrix <- read.csv(paste(di, homogenised_maps_folder, files[i], sep = ""), sep = ";", na.strings=c("","NA"), dec = ",")
  
  assign('map_concepts', as.character(my_matrix[,1])) # extract concept names
  my_matrix <- my_matrix[,-1] # discard first column for matrix (concept names)
  colnames(my_matrix) <- map_concepts # to avoid spaces being replaced by dots
  # rownames(my_matrix) <- map_concepts # duplicated rownames not allowed - to check whether this line is needed (then, avoid duplications by pre-collapsing matrices)
  
  # Built vector with all concepts (repetitions)
  all_concepts <- c(all_concepts, map_concepts) 
  
  for (g in 1:dim(my_matrix)[1]) {
    for (j in 1:dim(my_matrix)[2]) {
      ifelse(is.na(my_matrix[g, j]) == FALSE,
             all_relations <- rbind(all_relations,
                                  data.frame(matrix = i,
                                             source_label = colnames(my_matrix)[g],
                                             target_label = colnames(my_matrix)[j],
                                             weight = my_matrix[g, j])),
                                    "")
    }
  }
}
```

```{r}
write.table(all_relations, paste(di, output_folder, "4.1 all_relations.csv", sep = ""), sep = ";", row.names = FALSE)
```

- Build concepts dictionary

including column with number of occurrences

```{r}
concept_ocurrences <- data.frame(Label = all_concepts)

concept_ocurrences <- concept_ocurrences %>%
  group_by(Label) %>%
  summarise(occurrence = n())

my_concepts_dic <- concept_ocurrences %>%
  mutate(ID = 1:length(concept_ocurrences$Label))
```

- Add column with concept type

```{r}
concepts_class <- read.csv(paste(di, input_folder, "concepts_classification.csv", sep = ""), sep = ";", na.strings=c("","NA"), dec = ",")

concepts_class <- concepts_class %>%
  mutate(Label = Save_copy) %>%
  select(Label, DPSIR)
```

- Merge occurrences with classification

```{r}
my_concepts_dic <- left_join(my_concepts_dic, concepts_class, by = "Label")
```

- Build relationships dictionary

```{r}
relations_dic <- all_relations %>%
  select(source_label, target_label, weight) %>%
  group_by(source_label, target_label) %>%
  summarise(mean = mean(weight),
            sd = sd(weight),
            minimum = min(weight),
            maximum = max(weight),
            cv = sd(weight)/mean(weight),
            occurrences = n()) %>%
  mutate(sign_change = ifelse(minimum * maximum < 0,
                              "YES",
                              "NO"))
```

- Build file for Gephi

```{r}
Source <- as.vector(relations_dic$source_label)
Target <- as.vector(relations_dic$target_label)

for (i in 1:length(my_concepts_dic$ID)) {
  Source[which(Source == my_concepts_dic$Label[i], arr.ind = TRUE)] <- i
  Target[which(Target == my_concepts_dic$Label[i], arr.ind = TRUE)] <- i
}

relations_dic <- cbind(relations_dic, Source_ID = Source, Target_ID = Target)

edges_table_agg <- relations_dic %>%
  mutate(Weight = mean,
         Source = Source_ID,
         Target = Target_ID)

edges_table_agg <- edges_table_agg[,c(13,14,12,8,4,5,6,7,9)]

# Add column of weight type and modify weight to absolute weight - (for arrows thickness)
edges_table_agg$Weight_type <- c()
for (h in 1:length(edges_table_agg$Weight)) {
    ifelse(edges_table_agg$Weight[h] < 0,
           edges_table_agg$Weight_type[h] <- "negative",
           edges_table_agg$Weight_type[h] <- "positive")
    }
edges_table_agg$Weight <- abs(edges_table_agg$Weight)

# Add column marking occurrences above 1
edges_table_agg$occurrences_above1 <- c()
for (j in 1:length(edges_table_agg$Weight)) {
    ifelse(edges_table_agg$occurrences[j] > 1,
           edges_table_agg$occurrences_above1[j] <- 1,
           edges_table_agg$occurrences_above1[j] <- 0)
    }

edges_table_agg <- rbind(edges_table_agg, c(NA, NA, 0), c(NA, NA, 1)) # Add empty edges to consider thickness scale 0-1
```

- Export dictionaries and gephi files

```{r}
# dictionaries
write.table(relations_dic, paste(di, output_folder, "4.2 agg_relations_dic.csv", sep = ""), sep = ";", row.names = FALSE)
write.table(my_concepts_dic, paste(di, output_folder, "4.3 agg_concepts_dic.csv", sep = ""), sep = ";", row.names = FALSE)

# gephi files
write.table(my_concepts_dic, paste(di, gephi_output_folder, "nodes_table_agg.csv", sep = ""), sep = ";", row.names = FALSE)
write.table(edges_table_agg, paste(di, gephi_output_folder, "edges_table_agg.csv", sep = ""), sep = ";", row.names = FALSE)
```
