---
title: "Aggregated matrix analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(reshape)
library(FCMapper)
library(ggplot2)
library(dplyr)

di <- "/Users/maria.suarez.munoz/Google Drive/ms_FuzzyCognitiveMapping/FCM_analysis" # Mac

files_folder <- "output_files"
input_folder <- "input_files"
output_folder <- "/output_files/"
```

Load files

```{r}
concepts_dic <- read.csv(paste(di, files_folder, "4.3 agg_concepts_dic.csv", sep = "/"), sep = ";")
relations_dic <- read.csv(paste(di, files_folder, "4.2 agg_relations_dic.csv", sep = "/"), sep = ";")
```

# Relationships analysis

Plot: Histogram with number of relationships which occurred 1, 2, 3,... times (nr of occurrences of relationships per nr of times) - See Olazabal_2018 for interpretation (section "Individual maps after homogenisation")

```{r}
occurrences_tb <- data.frame(occurrences = as.factor(relations_dic$occurrences)) # extract number of occurrences per relationships (Source-Target)

occurrences_count <- occurrences_tb %>%
  group_by(occurrences) %>%
  summarise(count = n())

occurrences_count$count # how many relationships happened
occurrences_count$occurrences # what number of times

occ_melted <- melt(occurrences_count)

write.csv(occ_melted, paste(di, output_folder, "5.0 occ_melted.csv", sep = ""), sep = ";")

ggplot(occ_melted, aes(x = occurrences, y = value)) +
  geom_col() +
  theme_minimal() +
  xlab("What number of times") +
  ylab("How many relationships happened")
```

*Analyse types of relationships: % negative vs positive, occurrences, sd of the weights, sign changes, % strong vs weak weights...*

# Build aggregated matrix

```{r}
empty_agg_matrix <- data.frame(matrix(NA, 
                                      nrow = length(concepts_dic$ID), 
                                      ncol = length(concepts_dic$ID)))
colnames(empty_agg_matrix) <- concepts_dic$Label
rownames(empty_agg_matrix) <- concepts_dic$Label
```

Fill in empty agg matrix 

for (i in 1:length(relations_dic$source_label)), find coordinate (x,y) in agg_matrix, being x relations_dic$Source_ID[i] and y relations_dic$Target_ID[i], and give it value relations_dic$mean[i]
  
```{r}
agg_matrix <- empty_agg_matrix
for (i in 1:length(relations_dic$source_label)) {
# for (i in 1:5) {
  x <- as.numeric(relations_dic$Source_ID[i])
  y <- as.numeric(relations_dic$Target_ID[i])
  # weight_value <- relations_dic$mean[i]
  agg_matrix[x, y] <- relations_dic$mean[i]
}
```


```{r}
write.table(agg_matrix, paste(di, output_folder, "5.1 agg_matrix.csv", sep = ""), sep = ";", row.names = TRUE)
```

# Matrix indices
 
```{r, echo = FALSE}
agg_matrix[is.na(agg_matrix)] <- 0

# write.table(agg_matrix, paste(di, output_folder, "5.1 agg_matrix_0values.csv", sep = ""), sep = ";", row.names = TRUE) # Export agg_matrix for FCMapper (0 values instead of NA)

agg_matrix_indices <- matrix.indices(as.matrix(agg_matrix)) #FCMapper

D_self <- as.numeric(agg_matrix_indices$Value[1]) / as.numeric(agg_matrix_indices$Value[3])^2
Percentage_T <- as.numeric(agg_matrix_indices$Value[4]) * 100 / as.numeric(agg_matrix_indices$Value[3])
Percentage_R <- as.numeric(agg_matrix_indices$Value[5]) * 100 / as.numeric(agg_matrix_indices$Value[3])
Percentage_O <- as.numeric(agg_matrix_indices$Value[7]) * 100 / as.numeric(agg_matrix_indices$Value[3])
  
agg_matrix_indices$Index <- as.character(agg_matrix_indices$Index)
agg_matrix_indices <- rbind(agg_matrix_indices, c("Density with loops", D_self))
agg_matrix_indices <- rbind(agg_matrix_indices, c("Percentage_T", Percentage_T))
agg_matrix_indices <- rbind(agg_matrix_indices, c("Percentage_R", Percentage_R))
agg_matrix_indices <- rbind(agg_matrix_indices, c("Percentage_O", Percentage_O))

names <- agg_matrix_indices$Index
t_agg_matrix_indices <- t(as.matrix(agg_matrix_indices$Value))
colnames(t_agg_matrix_indices) <- names
```

```{r}
write.table(t_agg_matrix_indices, paste(di, output_folder, "5.2 agg_matrix_indices.csv", sep = ""), sep = ";", row.names = FALSE)
```

**Note on density**

Connection density = Number of connections / Number of concepts

Density as [@Ozesmi2004]: Number of connections / Number of possible connections
  with self loops: Number of connections / (Number of concepts^2)
  without self loops: Number of connections / (Number of concepts * (Number of concepts - 1))
  
We consider that self-loops are possible, and add this index in the table ("Density with loops")

# Concepts indices

Include also concept ocurrence (taken from my_concepts_dic)
```{r, echo = FALSE}
concept_indices <- concept.indices(agg_matrix, colnames(agg_matrix)) #FCMapper

occurrencestojoin <- data.frame(Concept = concepts_dic$Label, Occurrence = concepts_dic$occurrence)

concept_indices <- inner_join(concept_indices, occurrencestojoin, by = c("Concept"))
```

Include classification of each concept
```{r}
concepts_dic$Concept <- concepts_dic$Label
concept_indices <- left_join(concept_indices, concepts_dic)

concept_indices <- concept_indices %>%
  select(ID, Concept, DPSIR, Occurrence, Outdegree, Indegree, Centrality, Transmitter, Receiver, Ordinary)
```

```{r}
write.table(concept_indices, paste(di, output_folder, "5.3 agg_matrix_concept_indices.csv", sep = ""), sep = ";", row.names = FALSE)
```

## Plots

Plot: occurrences - centrality

*Nr occurrences of a concepts vs variable weighting its importance (degree, out/indegree, ...) - maybe need to "normalize" the importance --> next plot*

```{r}
plot(concept_indices$Occurrence, concept_indices$Centrality, xlab = "Concept occurrence", ylab = "Concept centrality", main = "Aggregated matrix")
```

Plot: occurrences - centrality/occurrences ("unbias" centrality)

```{r}
# plot(concept_indices$Occurrence, (concept_indices$Centrality/concept_indices$Occurrence))
```

Plot: Centrality value per concept differentiating between out and in degree

```{r}
degrees <- concept_indices %>%
  select(Concept, Outdegree, Indegree)

# degrees <- degrees[1:10,] # select only a few concepts

melted <- melt(degrees, id.vars=c("Concept"))
colnames(melted) <- c("Concept", "Variable", "Centrality")

melted <- within(melted, {
  Concept <- factor(Concept, levels = names(rev(sort(tapply(Centrality, Concept, sum)))))
})

ggplot(melted, aes(x= Concept, y = Centrality, fill = Variable)) + 
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))
```

Plot: Centrality value per concept differentiating between out and in degree - top 20% or whatever percentage of centrality

```{r}
n <- 10
title <- "Aggregated map"

filt_degrees <- concept_indices %>%
  select(Concept, Outdegree, Indegree, Centrality) %>%
  top_n(n, Centrality)

filt_degrees <- filt_degrees %>%
  select(Concept, Outdegree, Indegree)

filt_melted <- melt(filt_degrees, id.vars=c("Concept"))
colnames(filt_melted) <- c("Concept", "Variable", "Centrality")

filt_melted <- within(filt_melted, {
  Concept <- factor(Concept, levels = names(sort(tapply(Centrality, Concept, sum))))
})

ggplot(filt_melted, aes(x= Concept, y = Centrality, fill = Variable)) + 
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text()) +
  ggtitle(title) +
  coord_flip()
```

# Concepts classification analysis

```{r}
total_nr_concepts <- length(concepts_dic$Label)
dpsir_classes <- concepts_dic %>%
  select(DPSIR) %>%
  group_by(DPSIR) %>%
  summarise(abs_dpsir_classes = n()) %>%
  mutate(percentage_classes = (abs_dpsir_classes * 100) / total_nr_concepts)

# other_classes <- concepts_dic %>%
#   select(Posibilidad_B) %>%
#   group_by(Posibilidad_B) %>%
#   summarise(abs_other_classes = n()) %>%
#   mutate(percentage_classes = (abs_other_classes * 100) / total_nr_concepts)
```

Export

```{r}
write.table(dpsir_classes, paste(di, output_folder, "5.4 dpsir_concept_classification.csv", sep = ""), sep = ";", row.names = TRUE)

# write.table(other_classes, paste(di, output_folder, "5.5 other_concept_classification.csv", sep = ""), sep = ";", row.names = TRUE)
```

# DPSIR - R/T/O relationship

```{r}
RTO_DPSIR <- concept_indices %>% 
  mutate(RTO = ifelse(Ordinary == 1, "Ordinary", 
                      ifelse(Receiver == 1, "Receiver", 
                             ifelse(Transmitter == 1, "Transmitter", NA)))) %>%
  select(RTO, DPSIR) %>%
  group_by(RTO, DPSIR) %>%
  summarise(count = n())

plot(RTO_DPSIR$count)
```

