---
title: "Groups map analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)

di <- "/Users/maria.suarez.munoz/Google Drive/ms_FuzzyCognitiveMapping/FCM_analysis" # Mac

homogenised_maps_folder <- "input_files/homogenised_matrices/"
input_folder <- "/input_files/"
output_folder <- "/output_files/"
gephi_output_folder <- "/output_files/files_for_Gephi_plotting/aggregated/"

files <- list.files(paste(di, homogenised_maps_folder, sep = "/"), pattern = "*.csv")
```

Load reference table with stakeholders type:

```{r}
#OLD - stakeholders <- read.csv(paste(di, "input_files/interviews_info_clean.csv", sep = "/"), sep = ";", na.strings=c("","NA"), dec = ",")
stakeholders <- read.csv(paste(di, output_folder, "1.0. maps_to_matrices_ref_table.csv", sep = ""), sep = ";", na.strings=c("","NA"), dec = ",")

stakeholders <- stakeholders %>%
  mutate(ID_interview = Entrevista)
```

Build list of maps per stakeholder group
```{r}
researchers <- c()
forestry_managers <- c()
socioeconomic <- c()

for (i in 1:length(stakeholders$ID_interview)) {
  ifelse(stakeholders$Stakeholders_type[i] == "Researchers",
         researchers <- c(researchers, i),
         ifelse(stakeholders$Stakeholders_type[i] == "Forestry managers",
                forestry_managers <- c(forestry_managers, i),
                socioeconomic <- c(socioeconomic, i)))
}

#check
for (i in 1:length(researchers)) {print(files[researchers[i]])}
for (i in 1:length(forestry_managers)) {print(files[forestry_managers[i]])}
for (i in 1:length(socioeconomic)) {print(files[socioeconomic[i]])}
```

# Researchers aggregated map

```{r}
researchers_concepts <- c()
researchers_relations <- data.frame(matrix = integer(),
                            source_label = character(),
                            target_label = character(),
                            weight = numeric())

for (i in 1:length(researchers)) {
# for (i in 1:2) { # testing
  my_matrix <- read.csv(paste(di, homogenised_maps_folder, files[researchers[i]], sep = "/"), sep = ";", na.strings=c("","NA"), dec = ",")
  
  assign('researcher_map_concepts', as.character(my_matrix[,1])) # extract concept names
  my_matrix <- my_matrix[,-1] # discard first column for matrix (concept names)
  colnames(my_matrix) <- researcher_map_concepts # to avoid spaces being replaced by dots
  # rownames(my_matrix) <- researcher_map_concepts # duplicated rownames not allowed - to check whether this line is needed (then, avoid duplications by pre-collapsing matrices)
  
  # Built vector with all concepts (repetitions)
  researchers_concepts <- c(researchers_concepts, researcher_map_concepts) 
  
  for (g in 1:dim(my_matrix)[1]) {
    for (j in 1:dim(my_matrix)[2]) {
      ifelse(is.na(my_matrix[g, j]) == FALSE,
             researchers_relations <- rbind(researchers_relations,
                                  data.frame(matrix = i,
                                             source_label = colnames(my_matrix)[g],
                                             target_label = colnames(my_matrix)[j],
                                             weight = my_matrix[g, j])),
                                    "")
    }
  }
}
```

## Researchers concept occurrences

```{r}
researchers_occurrences <- data.frame(Label = researchers_concepts)

researchers_occurrences <- researchers_occurrences %>%
  group_by(Label) %>%
  summarise(researchers_occurrence = n())
```

- Add concept classification

```{r}
concepts_class <- read.csv(paste(di, input_folder, "concepts_classification.csv", sep = ""), sep = ";", na.strings=c("","NA"), dec = ",")
concepts_class <- concepts_class %>%
  mutate(Label = Save_copy) %>%
  select(Label, DPSIR)
```

- Merge occurrences with classification and add ID

```{r}
researchers_occurrences <- left_join(researchers_occurrences, concepts_class, by = "Label")

researchers_occurrences$ID <- 1:length(researchers_occurrences$Label)
```

## Researchers relationships

```{r}
researchers_rel_dic <- researchers_relations %>%
  select(source_label, target_label, weight) %>%
  group_by(source_label, target_label) %>%
  summarise(mean = mean(weight),
            sd = sd(weight),
            minimum = min(weight),
            maximum = max(weight),
            cv = sd(weight)/mean(weight),
            occurrences = n()) %>%
  mutate(sign_change = ifelse(minimum * maximum < 0,
                              "YES",
                              "NO"))
```

## Generate Gephi files for researchers matrix

```{r}
# Build file for Gephi
Source <- as.vector(researchers_rel_dic$source_label)
Target <- as.vector(researchers_rel_dic$target_label)

for (i in 1:length(researchers_occurrences$ID)) {
  Source[which(Source == researchers_occurrences$Label[i], arr.ind = TRUE)] <- i
  Target[which(Target == researchers_occurrences$Label[i], arr.ind = TRUE)] <- i
}

researchers_rel_dic <- cbind(researchers_rel_dic, Source_ID = Source, Target_ID = Target)

edges_table_researchers <- researchers_rel_dic %>%
  mutate(Weight = mean,
         Source = Source_ID,
         Target = Target_ID)

edges_table_researchers <- edges_table_researchers[,c(13,14,12)]

# Add column of weight type and modify weight to absolute weight - (for arrows thickness)

edges_table_researchers$Weight_type <- c()

for (h in 1:length(edges_table_researchers$Weight)) {
    ifelse(edges_table_researchers$Weight[h] < 0,
           edges_table_researchers$Weight_type[h] <- "negative",
           edges_table_researchers$Weight_type[h] <- "positive")
    }

edges_table_researchers$Weight <- abs(edges_table_researchers$Weight)
edges_table_researchers <- rbind(edges_table_researchers, c(NA, NA, 0), c(NA, NA, 1)) # Add empty edges to consider thickness scale 0-1
```

Export gephi files and dictionaries
```{r}
write.table(researchers_rel_dic, paste(di, output_folder, "7.1 researchers_relations_dic.csv", sep = ""), sep = ";", row.names = FALSE)
write.table(researchers_occurrences, paste(di, output_folder, "7.2 researchers_concepts_dic.csv", sep = ""), sep = ";", row.names = FALSE)

write.table(researchers_occurrences, paste(di, gephi_output_folder, "nodes_table_researchers.csv", sep = ""), sep = ";", row.names = FALSE)
write.table(edges_table_researchers, paste(di, gephi_output_folder, "edges_table_researchers.csv", sep = ""), sep = ";", row.names = FALSE)
```

# Forestry managers aggregated map

```{r}
managers_concepts <- c()
managers_relations <- data.frame(matrix = integer(),
                            source_label = character(),
                            target_label = character(),
                            weight = numeric())

for (i in 1:length(forestry_managers)) {
# for (i in 1:2) { # testing
  my_matrix <- read.csv(paste(di, homogenised_maps_folder, files[forestry_managers[i]], sep = "/"), sep = ";", na.strings=c("","NA"), dec = ",")
  
  assign('managers_map_concepts', as.character(my_matrix[,1])) # extract concept names
  my_matrix <- my_matrix[,-1] # discard first column for matrix (concept names)
  colnames(my_matrix) <- managers_map_concepts # to avoid spaces being replaced by dots
  # rownames(my_matrix) <- managers_map_concepts # duplicated rownames not allowed - to check whether this line is needed (then, avoid duplications by pre-collapsing matrices)
  
  # Built vector with all concepts (repetitions)
  managers_concepts <- c(managers_concepts, managers_map_concepts) 
  
  for (g in 1:dim(my_matrix)[1]) {
    for (j in 1:dim(my_matrix)[2]) {
      ifelse(is.na(my_matrix[g, j]) == FALSE,
             managers_relations <- rbind(managers_relations,
                                  data.frame(matrix = i,
                                             source_label = colnames(my_matrix)[g],
                                             target_label = colnames(my_matrix)[j],
                                             weight = my_matrix[g, j])),
                                    "")
    }
  }
}
```

## Managers concept occurrences

```{r}
managers_occurrences <- data.frame(Label = managers_concepts)

managers_occurrences <- managers_occurrences %>%
  group_by(Label) %>%
  summarise(managers_occurrence = n())

managers_occurrences$ID <- 1:length(managers_occurrences$Label)
```

- Add concept classification

- Merge occurrences with classification and add ID

```{r}
managers_occurrences <- left_join(managers_occurrences, concepts_class, by = "Label")

managers_occurrences$ID <- 1:length(managers_occurrences$Label)
```

## Managers relationships

```{r}
managers_rel_dic <- managers_relations %>%
  select(source_label, target_label, weight) %>%
  group_by(source_label, target_label) %>%
  summarise(mean = mean(weight),
            sd = sd(weight),
            minimum = min(weight),
            maximum = max(weight),
            cv = sd(weight)/mean(weight),
            occurrences = n()) %>%
  mutate(sign_change = ifelse(minimum * maximum < 0,
                              "YES",
                              "NO"))
```

## Generate Gephi files for managers matrix

```{r}
# Build file for Gephi
Source <- as.vector(managers_rel_dic$source_label)
Target <- as.vector(managers_rel_dic$target_label)

for (i in 1:length(managers_occurrences$ID)) {
  Source[which(Source == managers_occurrences$Label[i], arr.ind = TRUE)] <- i
  Target[which(Target == managers_occurrences$Label[i], arr.ind = TRUE)] <- i
}

managers_rel_dic <- cbind(managers_rel_dic, Source_ID = Source, Target_ID = Target)

edges_table_managers <- managers_rel_dic %>%
  mutate(Weight = mean,
         Source = Source_ID,
         Target = Target_ID)

edges_table_managers <- edges_table_managers[,c(13,14,12)]

# Add column of weight type and modify weight to absolute weight - (for arrows thickness)

edges_table_managers$Weight_type <- c()

for (h in 1:length(edges_table_managers$Weight)) {
    ifelse(edges_table_managers$Weight[h] < 0,
           edges_table_managers$Weight_type[h] <- "negative",
           edges_table_managers$Weight_type[h] <- "positive")
    }

edges_table_managers$Weight <- abs(edges_table_managers$Weight)
edges_table_managers <- rbind(edges_table_managers, c(NA, NA, 0), c(NA, NA, 1)) # Add empty edges to consider thickness scale 0-1
```

Export gephi files and dictionaries
```{r}
write.table(managers_rel_dic, paste(di, output_folder, "7.3 managers_rel_dic.csv", sep = ""), sep = ";", row.names = FALSE)
write.table(managers_occurrences, paste(di, output_folder, "7.4 managers_concepts_dic.csv", sep = ""), sep = ";", row.names = FALSE)

write.table(managers_occurrences, paste(di, gephi_output_folder, "nodes_managers.csv", sep = ""), sep = ";", row.names = FALSE)
write.table(edges_table_managers, paste(di, gephi_output_folder, "edges_table_managers.csv", sep = ""), sep = ";", row.names = FALSE)
```

# Socio-economic agents' aggregated map

```{r}
socioeconomic_concepts <- c()
socioeconomic_relations <- data.frame(matrix = integer(),
                            source_label = character(),
                            target_label = character(),
                            weight = numeric())

for (i in 1:length(socioeconomic)) {
# for (i in 1:2) { # testing
  my_matrix <- read.csv(paste(di, homogenised_maps_folder, files[socioeconomic[i]], sep = "/"), sep = ";", na.strings=c("","NA"), dec = ",")
  
  assign('socioeconomic_map_concepts', as.character(my_matrix[,1])) # extract concept names
  my_matrix <- my_matrix[,-1] # discard first column for matrix (concept names)
  colnames(my_matrix) <- socioeconomic_map_concepts # to avoid spaces being replaced by dots
  # rownames(my_matrix) <- others_map_concepts # duplicated rownames not allowed - to check whether this line is needed (then, avoid duplications by pre-collapsing matrices)
  
  # Built vector with all concepts (repetitions)
  socioeconomic_concepts <- c(socioeconomic_concepts, socioeconomic_map_concepts) 
  
  for (g in 1:dim(my_matrix)[1]) {
    for (j in 1:dim(my_matrix)[2]) {
      ifelse(is.na(my_matrix[g, j]) == FALSE,
             socioeconomic_relations <- rbind(socioeconomic_relations,
                                  data.frame(matrix = i,
                                             source_label = colnames(my_matrix)[g],
                                             target_label = colnames(my_matrix)[j],
                                             weight = my_matrix[g, j])),
                                    "")
    }
  }
}
```

## socioeconomic' concept occurrences

```{r}
socioeconomic_occurrences <- data.frame(Label = socioeconomic_concepts)

socioeconomic_occurrences <- socioeconomic_occurrences %>%
  group_by(Label) %>%
  summarise(socioeconomic_occurrence = n())

socioeconomic_occurrences$ID <- 1:length(socioeconomic_occurrences$Label)
```

- Add concept classification

- Merge occurrences with classification and add ID

```{r}
socioeconomic_occurrences <- left_join(socioeconomic_occurrences, concepts_class, by = "Label")

socioeconomic_occurrences$ID <- 1:length(socioeconomic_occurrences$Label)
```

## socioeconomic' relationships

```{r}
socioeconomic_rel_dic <- socioeconomic_relations %>%
  select(source_label, target_label, weight) %>%
  group_by(source_label, target_label) %>%
  summarise(mean = mean(weight),
            sd = sd(weight),
            minimum = min(weight),
            maximum = max(weight),
            cv = sd(weight)/mean(weight),
            occurrences = n()) %>%
  mutate(sign_change = ifelse(minimum * maximum < 0,
                              "YES",
                              "NO"))
```

## Generate Gephi files for locals matrix

```{r}
# Build file for Gephi
Source <- as.vector(socioeconomic_rel_dic$source_label)
Target <- as.vector(socioeconomic_rel_dic$target_label)

for (i in 1:length(socioeconomic_occurrences$ID)) {
  Source[which(Source == socioeconomic_occurrences$Label[i], arr.ind = TRUE)] <- i
  Target[which(Target == socioeconomic_occurrences$Label[i], arr.ind = TRUE)] <- i
}

socioeconomic_rel_dic <- cbind(socioeconomic_rel_dic, Source_ID = Source, Target_ID = Target)

edges_table_socioeconomic <- socioeconomic_rel_dic %>%
  mutate(Weight = mean,
         Source = Source_ID,
         Target = Target_ID)

edges_table_socioeconomic <- edges_table_socioeconomic[,c(13,14,12)]

# Add column of weight type and modify weight to absolute weight - (for arrows thickness)

edges_table_socioeconomic$Weight_type <- c()

for (h in 1:length(edges_table_socioeconomic$Weight)) {
    ifelse(edges_table_socioeconomic$Weight[h] < 0,
           edges_table_socioeconomic$Weight_type[h] <- "negative",
           edges_table_socioeconomic$Weight_type[h] <- "positive")
    }

edges_table_socioeconomic$Weight <- abs(edges_table_socioeconomic$Weight)
edges_table_socioeconomic <- rbind(edges_table_socioeconomic, c(NA, NA, 0), c(NA, NA, 1)) # Add empty edges to consider thickness scale 0-1
```

Export gephi files and relationship dictionary
```{r}
write.table(socioeconomic_rel_dic, paste(di, output_folder, "7.5 others_rel_dic.csv", sep = ""), sep = ";", row.names = FALSE)
write.table(socioeconomic_occurrences, paste(di, output_folder, "7.6 others_concepts_dic.csv", sep = ""), sep = ";", row.names = FALSE)

write.table(socioeconomic_occurrences, paste(di, gephi_output_folder, "nodes_others.csv", sep = ""), sep = ";", row.names = FALSE)
write.table(edges_table_socioeconomic, paste(di, gephi_output_folder, "edges_table_others.csv", sep = ""), sep = ";", row.names = FALSE)
```

# Concepts occurrences analysis

```{r}
per_group_occurrences <- full_join(researchers_occurrences, managers_occurrences, by = "Label")

per_group_occurrences <- full_join(per_group_occurrences, socioeconomic_occurrences, by = "Label")

per_group_occurrences$researchers_occurrence[is.na(per_group_occurrences$researchers_occurrence)] <- 0
per_group_occurrences$socioeconomic_occurrence[is.na(per_group_occurrences$socioeconomic_occurrence)] <- 0
per_group_occurrences$managers_occurrence[is.na(per_group_occurrences$managers_occurrence)] <- 0

per_group_occurrences <- per_group_occurrences %>%
  select(Label, researchers_occurrence, managers_occurrence, socioeconomic_occurrence)
```

Export per group occurrences table
```{r}
write.table(per_group_occurrences, paste(di, output_folder, "7.7 per_group_concept_occurrences.csv", sep = ""), sep = ";", row.names = TRUE)
```
