---
title: "Per group aggregated matrix analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(FCMapper)
library(dplyr)
library(ggplot2)
library(reshape)

di <- "/Users/maria.suarez.munoz/Google Drive/ms_FuzzyCognitiveMapping/FCM_analysis" # Mac
output_folder <- "/output_files/"
```

# Build researchers matrix

```{r}
# Load files
res_relations_dic <- read.csv(paste(di, output_folder, "7.1 researchers_relations_dic.csv", sep = ""), sep = ";")

res_concepts_dic <- read.csv(paste(di, output_folder, "7.2 researchers_concepts_dic.csv", sep = ""), sep = ";")

# Build empty matrix
empty_res_matrix <- data.frame(matrix(NA, nrow = length(res_concepts_dic$ID), ncol = length(res_concepts_dic$ID)))
colnames(empty_res_matrix) <- res_concepts_dic$Label
rownames(empty_res_matrix) <- res_concepts_dic$Label

# Fill in empty agg matrix
res_matrix <- empty_res_matrix
for (i in 1:length(res_relations_dic$source_label)) {
  x <- as.numeric(res_relations_dic$Source_ID[i])
  y <- as.numeric(res_relations_dic$Target_ID[i])
  res_matrix[x, y] <- res_relations_dic$mean[i]
}

res_matrix[is.na(res_matrix)] <- 0 # replace NA by 0

check.matrix(res_matrix) 
```

## Relationships histogram - Researchers' map

```{r}
occurrences_res <- data.frame(occurrences = as.factor(res_relations_dic$occurrences)) # extract number of occurrences per relationships (Source-Target)

occurrences_count_res <- occurrences_res %>%
  group_by(occurrences) %>%
  summarise(count = n())

occurrences_count_res$count # how many relationships happened
occurrences_count_res$occurrences # what number of times

occ_melted_res <- melt(occurrences_count_res)

ggplot(occ_melted_res, aes(x = occurrences, y = value)) +
  geom_col() +
  theme_minimal() +
  xlab("What number of times") +
  ylab("How many relationships happened") +
  ggtitle("Researchers")
```

# Build forestry managers matrix

```{r}
# Load files
man_relations_dic <- read.csv(paste(di, output_folder, "7.3 managers_rel_dic.csv", sep = ""), sep = ";")

man_concepts_dic <- read.csv(paste(di, output_folder, "7.4 managers_concepts_dic.csv", sep = ""), sep = ";")

# Build empty matrix
empty_man_matrix <- data.frame(matrix(NA, nrow = length(man_concepts_dic$ID), ncol = length(man_concepts_dic$ID)))
colnames(empty_man_matrix) <- man_concepts_dic$Label
rownames(empty_man_matrix) <- man_concepts_dic$Label

# Fill in empty agg matrix
man_matrix <- empty_man_matrix
for (i in 1:length(man_relations_dic$source_label)) {
  x <- as.numeric(man_relations_dic$Source_ID[i])
  y <- as.numeric(man_relations_dic$Target_ID[i])
  man_matrix[x, y] <- man_relations_dic$mean[i]
}

man_matrix[is.na(man_matrix)] <- 0 # replace NA by 0

check.matrix(man_matrix) 
```

## Relationships histogram - FM' map

```{r}
occurrences_man <- data.frame(occurrences = as.factor(man_relations_dic$occurrences)) # extract number of occurrences per relationships (Source-Target)

occurrences_count_man <- occurrences_man %>%
  group_by(occurrences) %>%
  summarise(count = n())

occurrences_count_man$count # how many relationships happened
occurrences_count_man$occurrences # what number of times

occ_melted_man <- melt(occurrences_count_man)

ggplot(occ_melted_man, aes(x = occurrences, y = value)) +
  geom_col() +
  theme_minimal() +
  xlab("What number of times") +
  ylab("How many relationships happened") +
  ggtitle("Forestry Managers")
```

# Build key stakeholders' matrix

```{r}
# Load files
others_relations_dic <- read.csv(paste(di, output_folder, "7.5 others_rel_dic.csv", sep = ""), sep = ";")

others_concepts_dic <- read.csv(paste(di, output_folder, "7.6 others_concepts_dic.csv", sep = ""), sep = ";")

# Build empty matrix
empty_others_matrix <- data.frame(matrix(NA, nrow = length(others_concepts_dic$ID), ncol = length(others_concepts_dic$ID)))
colnames(empty_others_matrix) <- others_concepts_dic$Label
rownames(empty_others_matrix) <- others_concepts_dic$Label

# Fill in empty agg matrix
others_matrix <- empty_others_matrix
for (i in 1:length(others_relations_dic$source_label)) {
  x <- as.numeric(others_relations_dic$Source_ID[i])
  y <- as.numeric(others_relations_dic$Target_ID[i])
  others_matrix[x, y] <- others_relations_dic$mean[i]
}

others_matrix[is.na(others_matrix)] <- 0 # replace NA by 0

check.matrix(others_matrix) 
```

## Relationships histogram - key stakeholders' map

```{r}
occurrences_others <- data.frame(occurrences = as.factor(others_relations_dic$occurrences)) # extract number of occurrences per relationships (Source-Target)

occurrences_count_others <- occurrences_others %>%
  group_by(occurrences) %>%
  summarise(count = n())

occurrences_count_others$count # how many relationships happened
occurrences_count_others$occurrences # what number of times

occ_melted_others <- melt(occurrences_count_others)

ggplot(occ_melted_others, aes(x = occurrences, y = value)) +
  geom_col() +
  theme_minimal() +
  xlab("What number of times") +
  ylab("How many relationships happened") +
  ggtitle("Other stakeholders")
```

# Analyse matrices

Matrices indices
```{r}
res_indices <- matrix.indices(res_matrix)
D_self <- as.numeric(res_indices$Value[1]) / as.numeric(res_indices$Value[3])^2
Percentage_T <- as.numeric(res_indices$Value[4]) * 100 / as.numeric(res_indices$Value[3])
Percentage_R <- as.numeric(res_indices$Value[5]) * 100 / as.numeric(res_indices$Value[3])
Percentage_O <- as.numeric(res_indices$Value[7]) * 100 / as.numeric(res_indices$Value[3])
  
res_indices$Index <- as.character(res_indices$Index)
res_indices <- rbind(res_indices, c("Density with loops", D_self))
res_indices <- rbind(res_indices, c("Percentage_T", Percentage_T))
res_indices <- rbind(res_indices, c("Percentage_R", Percentage_R))
res_indices <- rbind(res_indices, c("Percentage_O", Percentage_O))

man_indices <- matrix.indices(man_matrix)
D_self <- as.numeric(man_indices$Value[1]) / as.numeric(man_indices$Value[3])^2
Percentage_T <- as.numeric(man_indices$Value[4]) * 100 / as.numeric(man_indices$Value[3])
Percentage_R <- as.numeric(man_indices$Value[5]) * 100 / as.numeric(man_indices$Value[3])
Percentage_O <- as.numeric(man_indices$Value[7]) * 100 / as.numeric(man_indices$Value[3])

man_indices$Index <- as.character(man_indices$Index)
man_indices <- rbind(man_indices, c("Density with loops", D_self))
man_indices <- rbind(man_indices, c("Percentage_T", Percentage_T))
man_indices <- rbind(man_indices, c("Percentage_R", Percentage_R))
man_indices <- rbind(man_indices, c("Percentage_O", Percentage_O))

others_indices <- matrix.indices(others_matrix)
D_self <- as.numeric(others_indices$Value[1]) / as.numeric(others_indices$Value[3])^2
Percentage_T <- as.numeric(others_indices$Value[4]) * 100 / as.numeric(others_indices$Value[3])
Percentage_R <- as.numeric(others_indices$Value[5]) * 100 / as.numeric(others_indices$Value[3])
Percentage_O <- as.numeric(others_indices$Value[7]) * 100 / as.numeric(others_indices$Value[3])

others_indices$Index <- as.character(others_indices$Index)
others_indices <- rbind(others_indices, c("Density with loops", D_self))
others_indices <- rbind(others_indices, c("Percentage_T", Percentage_T))
others_indices <- rbind(others_indices, c("Percentage_R", Percentage_R))
others_indices <- rbind(others_indices, c("Percentage_O", Percentage_O))

per_group_indices <- data.frame(Index = res_indices$Index, Researchers_matrix = res_indices$Value, Managers_matrix = man_indices$Value, Others_matrix = others_indices$Value)
```

```{r}
write.table(per_group_indices, paste(di, output_folder, "8.1 per_group_matrices_indices.csv", sep = ""), sep = ";", row.names = TRUE)
```

Concepts indexes
```{r}
res_concept_indices <- concept.indices(res_matrix, colnames(res_matrix))
res_concept_indices <- res_concept_indices %>%
  mutate(Concept_R = Concept,
         Outdegre_R = Outdegree,
         Indegree_R = Indegree,
         Centrality_R = Centrality) %>%
  select(Concept_R, Outdegre_R, Indegree_R, Centrality_R)
  
man_concept_indices <- concept.indices(man_matrix, colnames(man_matrix))
man_concept_indices <- man_concept_indices %>%
   mutate(Concept_FM = Concept,
         Outdegre_FM = Outdegree,
         Indegree_FM = Indegree,
         Centrality_FM = Centrality) %>%
  select(Concept_FM, Outdegre_FM, Indegree_FM, Centrality_FM) 
  
others_concept_indices <- concept.indices(others_matrix, colnames(others_matrix))
others_concept_indices <- others_concept_indices %>%
   mutate(Concept_O = Concept,
         Outdegre_O = Outdegree,
         Indegree_O = Indegree,
         Centrality_O = Centrality) %>%
  select(Concept_O, Outdegre_O, Indegree_O, Centrality_O)
```

Merge concept indexes tables, including agg_matrix

```{r}
agg_concept_indices <- read.csv(paste(di, output_folder, "5.3 agg_matrix_concept_indices.csv", sep = ""), sep = ";")
agg_concept_indices <- agg_concept_indices %>%
   mutate(Outdegre_agg = Outdegree,
         Indegree_agg = Indegree,
         Centrality_agg = Centrality) %>%
  select(Concept, DPSIR, Outdegre_agg, Indegree_agg, Centrality_agg)  

concept_indices <- left_join(agg_concept_indices, res_concept_indices, by = c("Concept" = "Concept_R"))
concept_indices <- left_join(concept_indices, man_concept_indices, by = c("Concept" = "Concept_FM"))
concept_indices <- left_join(concept_indices, others_concept_indices, by = c("Concept" = "Concept_O"))
```

```{r}
write.table(concept_indices, paste(di, output_folder, "8.2 per_group_concept_indices.csv", sep = ""), sep = ";", row.names = TRUE)
```

Extract top X concepts per map (highest centrality values)
```{r}
nr_concepts <- 10

res_top_concepts <- res_concept_indices %>%
  filter(Centrality_R >= rev(sort(res_concept_indices$Centrality_R))[nr_concepts]) %>%
  select(Concept_R)

man_top_concepts <- man_concept_indices %>%
  filter(Centrality_FM >= rev(sort(man_concept_indices$Centrality_FM))[nr_concepts]) %>%
  select(Concept_FM)

others_top_concepts <- others_concept_indices %>%
  filter(Centrality_O >= rev(sort(others_concept_indices$Centrality_O))[nr_concepts]) %>%
  select(Concept_O)

top_concepts <- data.frame(researchers_top_concepts = sort(res_top_concepts$Concept), managers_top_concepts = sort(man_top_concepts$Concept), others_top_concepts = sort(others_top_concepts$Concept)) 
```

# In-/out-degree top concepts

## Researchers

```{r}
n <- 10 
title <- "Researchers' map"

filt_degrees <- res_concept_indices %>%
  select(Concept_R, Outdegre_R, Indegree_R, Centrality_R) %>%
  top_n(n, Centrality_R)

filt_degrees <- filt_degrees %>%
  select(Concept_R, Outdegre_R, Indegree_R)

filt_melted <- melt(filt_degrees, id.vars=c("Concept_R"))
colnames(filt_melted) <- c("Concept", "Variable", "Centrality")

filt_melted <- within(filt_melted, {
  Concept <- factor(Concept, levels = names(sort(tapply(Centrality, Concept, sum))))
})

ggplot(filt_melted, aes(x= Concept, y = Centrality, fill = Variable)) + 
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(), legend.position = "none") +
  ggtitle(title) +
  coord_flip()
```

## Forestry managers

```{r}
n <- 10 
title <- "Forestry managers' map"

filt_degrees <- man_concept_indices %>%
  select(Concept_FM, Outdegre_FM, Indegree_FM, Centrality_FM) %>%
  top_n(n, Centrality_FM)

filt_degrees <- filt_degrees %>%
  select(Concept_FM, Outdegre_FM, Indegree_FM)

filt_melted <- melt(filt_degrees, id.vars=c("Concept_FM"))
colnames(filt_melted) <- c("Concept", "Variable", "Centrality")

filt_melted <- within(filt_melted, {
  Concept <- factor(Concept, levels = names(sort(tapply(Centrality, Concept, sum))))
})

ggplot(filt_melted, aes(x= Concept, y = Centrality, fill = Variable)) + 
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(), legend.position = "none") +
  ggtitle(title) +
  coord_flip()
```

## Other stakeholders

```{r}
n <- 10 
title <- "Other stakeholders' map"

filt_degrees <- others_concept_indices %>%
  select(Concept_O, Outdegre_O, Indegree_O, Centrality_O) %>%
  top_n(n, Centrality_O)

filt_degrees <- filt_degrees %>%
  select(Concept_O, Outdegre_O, Indegree_O)

filt_melted <- melt(filt_degrees, id.vars=c("Concept_O"))
colnames(filt_melted) <- c("Concept", "Variable", "Centrality")

filt_melted <- within(filt_melted, {
  Concept <- factor(Concept, levels = names(sort(tapply(Centrality, Concept, sum))))
})

ggplot(filt_melted, aes(x= Concept, y = Centrality, fill = Variable)) + 
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(), legend.position = "none") +
  ggtitle(title) +
  coord_flip()
```

# Compare community matrices

Load aggregated matrix
```{r}
agg_matrix <- read.csv(paste(di, output_folder, "5.1 agg_matrix.csv", sep = "/"), sep = ";", na.strings = c("","NA"), dec = ",")
assign('concept_labels', row.names(agg_matrix)) # extract concept names
colnames(agg_matrix) <- concept_labels # to avoid spaces being replaced by dots
```

Compare community maps
```{r}
comp.maps(colnames(res_matrix), colnames(man_matrix))[2]
comp.maps(colnames(man_matrix), colnames(others_matrix))[2]
comp.maps(colnames(others_matrix), colnames(res_matrix))[2]

comp.maps(colnames(res_matrix), colnames(agg_matrix))[2]
comp.maps(colnames(man_matrix), colnames(agg_matrix))[2]
comp.maps(colnames(others_matrix), colnames(agg_matrix))[2]
```

# Concepts classification analysis

DPSIR classification
```{r}
res_total_nr_concepts <- length(res_concepts_dic$Label)
res_dpsir_classes <- res_concepts_dic %>%
  select(DPSIR) %>%
  group_by(DPSIR) %>%
  summarise(res_abs_classes = n()) %>%
  mutate(res_percentage_dpsir_classes = (res_abs_classes * 100) / res_total_nr_concepts)

man_total_nr_concepts <- length(man_concepts_dic$Label)
man_dpsir_classes <- man_concepts_dic %>%
  select(DPSIR) %>%
  group_by(DPSIR) %>%
  summarise(man_abs_classes = n()) %>%
  mutate(man_percentage_dpsir_classes = (man_abs_classes * 100) / man_total_nr_concepts)

other_total_nr_concepts <- length(others_concepts_dic$Label)
other_dpsir_classes <- others_concepts_dic %>%
  select(DPSIR) %>%
  group_by(DPSIR) %>%
  summarise(other_abs_classes = n()) %>%
  mutate(other_percentage_dpsir_classes = (other_abs_classes * 100) / other_total_nr_concepts)
                                       
per_group_dpsir_classification <- left_join(res_dpsir_classes, man_dpsir_classes)  
per_group_dpsir_classification <- left_join(per_group_dpsir_classification, other_dpsir_classes)
```

Other classification
```{r}
# res_other_classes <- res_concepts_dic %>%
#   select(Posibilidad_B) %>%
#   group_by(Posibilidad_B) %>%
#   summarise(res_abs_classes = n()) %>%
#   mutate(res_percentage_other_classes = (res_abs_classes * 100) / res_total_nr_concepts)
# 
# man_other_classes <- man_concepts_dic %>%
#   select(Posibilidad_B) %>%
#   group_by(Posibilidad_B) %>%
#   summarise(man_abs_classes = n()) %>%
#   mutate(man_percentage_other_classes = (man_abs_classes * 100) / man_total_nr_concepts)
# 
# other_other_classes <- others_concepts_dic %>%
#   select(Posibilidad_B) %>%
#   group_by(Posibilidad_B) %>%
#   summarise(other_abs_classes = n()) %>%
#   mutate(other_percentage_other_classes = (other_abs_classes * 100) / other_total_nr_concepts)
#                                        
# per_group_other_classification <- left_join(res_other_classes, man_other_classes)  
# per_group_other_classification <- left_join(per_group_other_classification, other_other_classes)
```

Export

```{r}
write.table(per_group_dpsir_classification, paste(di, output_folder, "8.3 per_group_dpsir_classification.csv", sep = ""), sep = ";", row.names = TRUE)

# write.table(per_group_other_classification, paste(di, output_folder, "8.4 per_group_other_classification.csv", sep = ""), sep = ";", row.names = TRUE)
```